Data Visualization

### 2018-11-04 scripts/3_data_prep.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

  suburb_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'melbSuburbs.shp')) %>%
    st_transform(crs=4283)
  sa1_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'sa1s.shp')) %>%
    st_transform(crs=4283)
  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach.shp')) %>%
    st_transform(crs=4283)

@@

@@

  # Add suburb designation and remove those that are outside   
   str_sf <- st_join(str_sf, 
                     suburb_sf %>% 
                      dplyr::select(suburb = NAME_2006,
                                    sub_des = suburbDesi,
                                    geometry)) %>%
   dplyr::filter(!is.na(sub_des))

   ltr_sf <- st_join(ltr_sf, 
                     suburb_sf %>% 
                       dplyr::select(suburb = NAME_2006,
                                     sub_des = suburbDesi,
                                     geometry)) %>%
   dplyr::filter(!is.na(sub_des))

@@

   # Add individual classes
   str_sf$geo_mrkt <- 'rural'
   str_sf$geo_mrkt[str_sf$sub_des == 'Middle'] <- 'suburban'
   str_sf$geo_mrkt[str_sf$sub_des == 'Inner'] <- 'city'
   str_sf$geo_mrkt[str_sf$suburb %in% core_suburbs] <- 'city-core'
   str_sf$geo_mrkt[str_sf$beach == 1] <- 'beach'

   # Order the factors properly
   str_sf$geo_mrkt <- factor(str_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))

@@

   # Add individual classes
   ltr_sf$geo_mrkt <- 'rural'
   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Middle'] <- 'suburban'
   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Inner'] <- 'city'
   ltr_sf$geo_mrkt[ltr_sf$suburb %in% core_suburbs] <- 'city-core'
   ltr_sf$geo_mrkt[ltr_sf$beach == 1] <- 'beach'

   # Order the factors properly
   ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban',
                                        'rural', 'beach'))

@@

Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties,

```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  # Calculate likely revenue
  str_tdf$lik_revenue_net <- ((str_tdf$lik_bookings * str_tdf$med_rate) -
                                (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd))

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_obj, core_suburbs,
        file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))

>>>>

  suburb_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'melbSuburbs.shp')) %>%
    st_transform(crs=4283)
  sa1_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'sa1s.shp')) %>%
    st_transform(crs=4283)
  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach_no_outer.shp')) %>%
    st_transform(crs=4283)

@@

### Host types

Finally, we test to see if grouping by hosts types has any impact.

First we must divide hosts up.  We start by looking at block rate.

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ggplot(str_tdf, aes(x=block_rate)) + 
    geom_density(fill=str_col, color=str_col) +
    ylab('Frequency\n') + 
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0,1,.2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
      ggtitle('Host Block Rate Frequency\n') +
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

We then add the number of blocked periods

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
    geom_point(fill=str_col, color=str_col, size=.2) +
    ylab('Nbr of Blocked Periods\n') + 
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

No real pattern emerges, so we divide manually.

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE}

  str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1)

  str_tdf$host_type <- 'Unknown'
  #str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
  # str_tdf$host_type <- factor(str_tdf$host_type,
  #                             levels=c('Profit Seeker', 'Opportunistic Sharer', 
  #                                       'Multi-Platform User', 'Unknown'))
  str_tdf$host_type <- factor(str_tdf$host_type,
                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                       'Unknown'))

 ggplot(str_tdf, 
       aes(x=block_rate, y=blockpertime, color=host_type)) + 
  geom_point(alpha=.5, size=.8, shape=16) +
  ylab('Number of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

    scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7])) + 
    theme(legend.position='bottom',
           legend.title = element_blank(),
         plot.title = element_text(hjust = 0.5))+
     guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1)))

 str_tdf_all <- str_tdf
 str_tdf <- str_tdf %>% dplyr::filter(host_type == 'Profit Seeker')

@@

  # Add suburb designation and remove those that are outside   
   str_sf <- st_join(str_sf, 
                     suburb_sf %>% 
                      dplyr::select(suburb = NAME_2006,
                                    sub_des = suburbDesi,
                                    geometry)) %>%
   dplyr::filter(!is.na(sub_des) & sub_des != 'Outer')

   ltr_sf <- st_join(ltr_sf, 
                     suburb_sf %>% 
                       dplyr::select(suburb = NAME_2006,
                                     sub_des = suburbDesi,
                                     geometry)) %>%
   dplyr::filter(!is.na(sub_des) & sub_des != 'Outer')

@@

   # Add individual classes
   str_sf$geo_mrkt <- 'suburban'
   str_sf$geo_mrkt[str_sf$sub_des == 'Inner'] <- 'city'
   str_sf$geo_mrkt[str_sf$suburb %in% core_suburbs] <- 'city-core'
   str_sf$geo_mrkt[str_sf$beach == 1] <- 'beach'

   # Order the factors properly
   str_sf$geo_mrkt <- factor(str_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban', 'beach'))

@@

   # Add individual classes
   ltr_sf$geo_mrkt <- 'suburban'
   ltr_sf$geo_mrkt[ltr_sf$sub_des == 'Inner'] <- 'city'
   ltr_sf$geo_mrkt[ltr_sf$suburb %in% core_suburbs] <- 'city-core'
   ltr_sf$geo_mrkt[ltr_sf$beach == 1] <- 'beach'

   # Order the factors properly
   ltr_sf$geo_mrkt <- factor(ltr_sf$geo_mrkt,
                               levels=c('city-core', 'city', 'suburban', 'beach'))

@@

<!-- Next we create Likely Revenue, by imputing occupancy rates and revenues for the remainder of the year for those properties, -->

<!-- ```{r lik_revenues, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   # Calculate likely revenue -->
<!--   str_tdf$lik_revenue_net <- ((str_tdf$lik_bookings * str_tdf$med_rate) - -->
<!--                                 (str_tdf$lik_bookings * str_tdf$avg_guests * cpppd)) -->

<!-- ``` -->

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_obj, core_suburbs, str_tdf_all,
        file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))

### 2018-11-04 scripts/4_data_analysis.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

@@

  # Extract out DFs (only those that imputed)
  str_tdf <- str_tdf %>%
    dplyr::left_join(imp_df, by='property_id') %>%
    dplyr::mutate(act_pref = ifelse(revenue_net > ltr_imp_revenue, 1, 0),
                  lik_pref = ifelse(lik_revenue_net > ltr_imp_revenue, 1, 0),
                  pot_pref = ifelse(pot_revenue_net > ltr_imp_revenue, 1, 0))

@@

  glm_lik_str <- glm(lik_pref ~ type + as.factor(bedbath),
                     family=binomial(link='logit'),
                     data=str_tdf)

  glm_pot_str <- glm(pot_pref~type+as.factor(bedbath),
                       family=binomial(link='logit'),
                       data=str_tdf)
```

@@

  glm_lik_loc <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt),
                     family=binomial(link='logit'),
                     data=str_tdf)

  glm_pot_loc <- glm(pot_pref ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                     family=binomial(link='logit'),
                     data=str_tdf)
```

@@

  glm_lik_host <- glm(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        guest_per_bed + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)

  glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)

  lik_glms <- list(str=glm_lik_str,
                   loc=glm_lik_loc,
                   host=glm_lik_host)

  pot_glms <- list(str=glm_pot_str,
                   loc=glm_pot_loc,
                   host=glm_pot_host)

@@

### Host types

Finally, we test to see if grouping by hosts types has any impact.

First we must divide hosts up.  We start by looking at block rate.

  ggplot(str_tdf, aes(x=block_rate)) + 
    geom_density(fill=str_col, color=str_col) +
    ylab('Frequency\n') + 
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0,1,.2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
      ggtitle('Host Block Rate Frequency\n') +
      theme(plot.title = element_text(hjust = 0.5)) +
      theme(axis.text.y=element_blank(),
          axis.ticks.y=element_blank())

@@

We then add the number of blocked periods

  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
    geom_point(fill=str_col, color=str_col, size=.2) +
    ylab('Nbr of Blocked Periods\n') + 
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

No real pattern emerges, so we divide manually.

  str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1)

  str_tdf$host_type <- 'Unknown'
  str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User'
  str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker'
  str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer'
  str_tdf$host_type <- factor(str_tdf$host_type,
                              levels=c('Profit Seeker', 'Opportunistic Sharer', 
                                        'Multi-Platform User', 'Unknown'))

 ggplot(str_tdf, 
       aes(x=block_rate, y=blockpertime, color=host_type)) + 
  geom_point(alpha=.5, size=.8, shape=16) +
  ylab('Number of Blocked Periods\n') + 
  xlab('\n% of Time Property is Blocked') +
      ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

    scale_x_continuous(breaks=seq(0, 1, .2),
                     labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
                                col_df$rgb[9])) + 
    theme(legend.position='bottom',
           legend.title = element_blank(),
         plot.title = element_text(hjust = 0.5))+
     guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1)))

And re-run the logistic regression models.

  ht_. <- split(str_tdf, str_tdf$host_type)

  lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))

  pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                          guest_per_bed + min_stay + I(canc_policy == 'Flexible'))

  lik_ht_glms <- purrr::map(ht_.,
                         .f=glm,
                         formula=lik_spec,
                         family=binomial(link='logit'))

  pot_ht_glms <- purrr::map(ht_.,
                         .f=glm,
                         formula=pot_spec,
                         family=binomial(link='logit'))

  dir.create(file.path(getwd(), 'data', 'analyzed'))
  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, pot_ht_glms, lik_glms, lik_ht_glms, core_suburbs,
       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

>>>>

  kimp_df <- knnImputeWrap(ltr_df = ltr_df, 
                           str_df = str_tdf,
                           knns = c(7,7))

  imp_df$ltr_imp_revenueK <- kimp_df$year[match(imp_df$property_id,
                                               kimp_df$property_id)]
  imp_df <- imp_df %>%
    rename(ltr_imp_revenueH = ltr_imp_revenue) %>%
    mutate(ltr_imp_revenueK = ((365-imp_dom)/365) * ltr_imp_revenueK,
           ltr_imp_revenue = .5 * (ltr_imp_revenueH + ltr_imp_revenueK))
  imp_df <- imp_df %>%
    left_join(str_tdf %>%
                dplyr::select(property_id, bedrooms, bathrooms, type, latitude,
                              longitude),
              by='property_id')

    save(imp_df, file=file.path(getwd(), 'data', 'analyzed', 'reviewers.RData'))

@@

  # Extract out DFs (only those that imputed)
  str_tdf <- str_tdf %>%
    dplyr::left_join(imp_df %>%
                       dplyr::select(-c(bedrooms, bathrooms, type, latitude, longitude)),
                     by='property_id') %>%
    dplyr::mutate(act_pref = ifelse(revenue_net > ltr_imp_revenue, 1, 0),
                  # lik_pref = ifelse(lik_revenue_net > ltr_imp_revenue, 1, 0),
                  pot_pref = ifelse(pot_revenue_net > ltr_imp_revenue, 1, 0),
                  pot_pref_mc = ifelse(pot_revenue_net * .85 > ltr_imp_revenue, 1, 0),
                  pot_pref_us = ifelse(pot_revenue_net > ltr_imp_revenue * .85, 1, 0))

@@

  glm_pot_str <- glm(pot_pref~type+as.factor(bedbath),
                       family=binomial(link='logit'),
                       data=str_tdf)
  glm_pot_str_mc <- glm(pot_pref_mc~type+as.factor(bedbath),
                       family=binomial(link='logit'),
                       data=str_tdf)
  glm_pot_str_us <- glm(pot_pref_us~type+as.factor(bedbath),
                       family=binomial(link='logit'),
                       data=str_tdf)

@@

  glm_pot_loc <- glm(pot_pref ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                     family=binomial(link='logit'),
                     data=str_tdf)
  glm_pot_loc_mc <- glm(pot_pref_mc ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                     family=binomial(link='logit'),
                     data=str_tdf)
  glm_pot_loc_us <- glm(pot_pref_us ~ type + as.factor(bedbath)+ as.factor(geo_mrkt),
                     family=binomial(link='logit'),
                     data=str_tdf)
```

@@

  glm_pot_host <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)
  glm_pot_host_mc <- glm(pot_pref_mc ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)
  glm_pot_host_us <- glm(pot_pref_us ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                        I(max_guests/bedrooms) + min_stay + I(canc_policy == 'Flexible'),
                      family=binomial(link='logit'),
                      data=str_tdf)

  pot_glms <- list(str=glm_pot_str,
                   loc=glm_pot_loc,
                   host=glm_pot_host)
  pot_mc_glms <- list(str=glm_pot_str_mc,
                   loc=glm_pot_loc_mc,
                   host=glm_pot_host_mc)
  pot_us_glms <- list(str=glm_pot_str_us,
                   loc=glm_pot_loc_us,
                   host=glm_pot_host_us)

@@

<!-- ### Host types -->

<!-- Finally, we test to see if grouping by hosts types has any impact.   -->

<!-- First we must divide hosts up.  We start by looking at block rate.   -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   ggplot(str_tdf, aes(x=block_rate)) +  -->
<!--     geom_density(fill=str_col, color=str_col) + -->
<!--     ylab('Frequency\n') +  -->
<!--     xlab('\n% of Time Property is Blocked') + -->
<!--     scale_x_continuous(breaks=seq(0,1,.2), -->
<!--                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
<!--       ggtitle('Host Block Rate Frequency\n') + -->
<!--       theme(plot.title = element_text(hjust = 0.5)) + -->
<!--       theme(axis.text.y=element_blank(), -->
<!--           axis.ticks.y=element_blank()) -->

<!-- ``` -->

<!-- We then add the number of blocked periods -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) +  -->
<!--     geom_point(fill=str_col, color=str_col, size=.2) + -->
<!--     ylab('Nbr of Blocked Periods\n') +  -->
<!--     xlab('\n% of Time Property is Blocked') + -->
<!--     scale_x_continuous(breaks=seq(0, 1, .2), -->
<!--                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
<!--     ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') + -->
<!--     theme(plot.title = element_text(hjust = 0.5))  -->

<!-- ``` -->

<!-- No real pattern emerges, so we divide manually.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   str_tdf$blockpertime <- round(str_tdf$nbr_block * (366 / str_tdf$total_days), 1) -->

<!--   str_tdf$host_type <- 'Unknown' -->
<!--   str_tdf$host_type[str_tdf$blockpertime > 12] <- 'Multi-Platform User' -->
<!--   str_tdf$host_type[str_tdf$block_rate <= .25] <- 'Profit Seeker' -->
<!--   str_tdf$host_type[str_tdf$block_rate >= .75] <- 'Opportunistic Sharer' -->
<!--   str_tdf$host_type <- factor(str_tdf$host_type, -->
<!--                               levels=c('Profit Seeker', 'Opportunistic Sharer',  -->
<!--                                         'Multi-Platform User', 'Unknown')) -->

<!--  ggplot(str_tdf,  -->
<!--        aes(x=block_rate, y=blockpertime, color=host_type)) +  -->
<!--   geom_point(alpha=.5, size=.8, shape=16) + -->
<!--   ylab('Number of Blocked Periods\n') +  -->
<!--   xlab('\n% of Time Property is Blocked') + -->
<!--       ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') + -->

<!--     scale_x_continuous(breaks=seq(0, 1, .2), -->
<!--                      labels=c('0%', '20%', '40%', '60%', '80%', '100%')) + -->
<!--     scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7],  -->
<!--                                 col_df$rgb[9])) +  -->
<!--     theme(legend.position='bottom', -->
<!--            legend.title = element_blank(), -->
<!--          plot.title = element_text(hjust = 0.5))+ -->
<!--      guides(colour = guide_legend(override.aes = list(size=3, -->
<!--                                                      alpha=1))) -->

<!-- ``` -->

<!-- And re-run the logistic regression models.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   ht_. <- split(str_tdf, str_tdf$host_type) -->

<!--   lik_spec <- as.formula(lik_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) + -->
<!--                           guest_per_bed + min_stay + I(canc_policy == 'Flexible')) -->

<!--   pot_spec <- as.formula(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) + -->
<!--                           guest_per_bed + min_stay + I(canc_policy == 'Flexible')) -->

<!--   lik_ht_glms <- purrr::map(ht_., -->
<!--                          .f=glm, -->
<!--                          formula=lik_spec, -->
<!--                          family=binomial(link='logit')) -->

<!--   pot_ht_glms <- purrr::map(ht_., -->
<!--                          .f=glm, -->
<!--                          formula=pot_spec, -->
<!--                          family=binomial(link='logit')) -->

<!-- ``` -->

```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  dir.create(file.path(getwd(), 'data', 'analyzed'))
  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, core_suburbs, str_tdf_all, pot_mc_glms, pot_us_glms,
       #pot_ht_glms, lik_ht_glms,
       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

  save(ltr_df, file=file.path(getwd(), 'data', 'analyzed', 'reviewers.RData'))

@@

### 2018-11-04 scripts/5_data_viz.Rmd
Update to geographic sample, models, host, etc.  Rough draft.

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, revenue=lik_revenue_net) %>%
                         dplyr::mutate(tenure = 'Short Term (Likely)   ',
                                       alpha = .5),
                       str_tdf %>% 
                         dplyr::select(type, revenue=pot_revenue_net) %>%
                         dplyr::mutate(tenure = 'Short Term (Potential)   ',
                                       alpha = .4),
                       ltr_df %>%
                         dplyr::select(type, revenue=gross_revenue) %>%
                         dplyr::mutate(tenure = 'Long-Term   ',
                                       alpha = .9))

@@

  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
     geom_density(fill=str.col, color=str.col) +
     ylab('Frequency\n') +
     xlab('\n% of Time Property is Blocked') +
     scale_x_continuous(breaks=seq(0,1,.2),
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
     #ggtitle('Host Block Rate Frequency\n') +
     theme(plot.title = element_text(hjust = 0.5)) +
     theme(axis.text.y=element_blank(),
           axis.ticks.y=element_blank())

  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) +
    geom_point(fill=str.col, color=str.col, size=.2) +
    ylab('Nbr of Blocked Periods\n') +
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  base.host <- ggplot(str_tdf,
                    aes(x=block_rate, y=blockpertime)) +
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') +
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%',
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4],
                #                            abb.col[7], abb.col[9])) +
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))

   ps.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  mu.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
               size=.4)  +
    ggtitle('Multi-Platform User')

  un.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

  png(filename = file.path(getwd(), 'images', "host_scat.png"), 
       width = 5.5, height = 3, units = 'in', res = 300)

    ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)

@@

 ggplot(str_tdf, aes(host_type, fill=host_type)) +
    geom_bar() +
    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
                               col_df$rgb[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') +
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
    #ggtitle('short-term Host Types') +
    theme(plot.title = element_text(hjust = 0.5))

>>>>

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, revenue=revenue_net) %>%
                         dplyr::mutate(tenure = '  Short Term (Actual)   ',
                                       alpha = .5),
                       str_tdf %>% 
                         dplyr::select(type, revenue=pot_revenue_net) %>%
                         dplyr::mutate(tenure = '  Short Term (Potential)   ',
                                       alpha = .4),
                       ltr_df %>%
                         dplyr::select(type, revenue=gross_revenue) %>%
                         dplyr::mutate(tenure = '  Long-Term   ',
                                       alpha = .9))

@@

  host.block.freq <- ggplot(str_tdf_all, aes(x=block_rate)) +
     geom_density(fill=str.col, color=str.col) +
     ylab('Frequency\n') +
     xlab('\n% of Time Property is Blocked') +
     scale_x_continuous(breaks=seq(0,1,.2),
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
     #ggtitle('Host Block Rate Frequency\n') +
     theme(plot.title = element_text(hjust = 0.5)) +
     theme(axis.text.y=element_blank(),
           axis.ticks.y=element_blank())

  block.rate.period <- ggplot(str_tdf_all, aes(x=block_rate, y=nbr_block * (366/total_days))) +
    geom_point(fill=str.col, color=str.col, size=.2) +
    ylab('Nbr of Blocked Periods\n') +
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

@@

  base.host <- ggplot(str_tdf_all,
                    aes(x=block_rate, y=blockpertime)) +
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') +
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%',
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4],
                #                            abb.col[7], abb.col[9])) +
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))

   ps.host <- base.host +
    geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host +
    geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Opportunistic Sharer', ],
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  # mu.host <- base.host +
  #   geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Multi-Platform User', ],
  #              size=.4)  +
  #   ggtitle('Multi-Platform User')

  un.host <- base.host +
    geom_point(data=str_tdf_all[str_tdf_all$host_type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

  png(filename = file.path(getwd(), 'images', "host_scat.png"), 
       width = 4, height = 6.5, units = 'in', res = 300)

    ggMultiPlots(ps.host, un.host, os.host, cols=1)

@@

 ggplot(str_tdf_all, aes(host_type, fill=host_type)) +
    geom_bar() +
    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') +
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit-Seekers','Opportunistic Sharers','Unknowns'))+
    #ggtitle('short-term Host Types') +
    theme(plot.title = element_text(hjust = 0.5))
